Pre-registration

### 2020-04-22 docs/preanalisis.Rmd

---
title: "Pre-registration"
csl: "../input/bib/apa6.csl"
bibliography: "../input/bib/zlibrary.bib"
# css: "../input/bib/style.css"
output:
  pdf_document:
    keep_tex: false
    template: null
    number_sections: true
    toc: true
  html_document:
    number_sections: true
    toc: true
    toc_float: true
    smart: false
geometry: margin=0.78in
header-includes:
  # - \usepackage[spanish,es-tabla,es-nodecimaldot]{babel}
  - \usepackage{caption}
  - \captionsetup[figure, table]{labelfont={bf},labelformat={default},labelsep=period}
  - \usepackage{graphicx}
  - \usepackage{float}
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{array}
  - \usepackage{multirow}
  - \usepackage{wrapfig}
  - \usepackage{float}
  - \usepackage{colortbl}
  - \usepackage{pdflscape}
  - \usepackage{tabu}
  - \usepackage{threeparttable}
linestretch: '1.5'
link-citations: yes
linkcolor: blue
---

>>>>

---
title: "Pre-registration"
csl: "../input/bib/apa6.csl"
bibliography: "../input/bib/zlibrary.bib"
# css: "../input/bib/style.css"
output:
  # pdf_document:
  #   keep_tex: false
  #   template: null
  #   number_sections: true
  #   toc: true
  html_document:
    number_sections: true
    toc: true
    toc_float: true
    smart: false
geometry: margin=0.78in
header-includes:
  # - \usepackage[spanish,es-tabla,es-nodecimaldot]{babel}
  - \usepackage{caption}
  - \captionsetup[figure, table]{labelfont={bf},labelformat={default},labelsep=period}
  - \usepackage{graphicx}
  - \usepackage{float}
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{array}
  - \usepackage{multirow}
  - \usepackage{wrapfig}
  - \usepackage{float}
  - \usepackage{colortbl}
  - \usepackage{pdflscape}
  - \usepackage{tabu}
  - \usepackage{threeparttable}
linestretch: '1.5'
link-citations: yes
linkcolor: blue
---
